### 2008-12-14 simplex-method.tkz.tex
Antigradient direction

\begin{figure}[!thb]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      x=1.5cm, y=1.5cm,
      xlabel=$x_1$,
      ylabel=$x_2$,
      xtick={1, 2, 3, 4, 5, 6},
      ytick={1, 3, 4, 5},
      xmin=-2, ymin=-1,
      xmax=7, ymax=7,
      axis x line=center,
      axis y line=center,
      pattern color=gray,
      area legend]

      \addplot[draw=none,mark=none,pattern=dots]
      coordinates{(0,0) (0,2) (2,3.5) (5,0)} \closedcycle;
      \label{plot:simplex-feasible-space}

      \draw[arrows=-triangle 60, dashed, ultra thick]
      (axis cs:1.5, 0.75) -- (axis cs:2.25,2.25);
      \label{plot:simplex-antigrow}

      \input{simplex_prob-contours.tkz.tex}

      \draw[thick] (axis cs:-1, 1.25)--(axis cs:4, 5)
      node [sloped,above,pos=0.85] {$-3x_1+4x_2 = 8$};
      \draw[thick,mark=none] (axis cs:1.5, 4.0833)--(axis cs:5.5, -0.5833)
      node [sloped,above,pos=0.5] {\contour{white}{$7x_1+6x_2=35$}};

      \draw node[circle, fill=black, scale=0.5, 
                 pin={above:\contour{white}{$(2, 3.5)$}}] at (axis cs:2,3.5) {};
      \draw node[circle, fill=black, scale=0.5, 
                 pin={left:$(0, 2)$}] at (axis cs:0,2) {};

      \addplot[ultra thick, arrows=-triangle 45, blue] coordinates{(0, 0) (0, 2)};
      \addplot[ultra thick, arrows=-triangle 45, blue] coordinates{(0, 2) (2,3.5)};
    \end{axis}
  \end{tikzpicture}
  \caption[Симплекс-метод]{Ход решения задачи \eqref{eq:lp-simple}
    симплекс-методом}
  \label{fig:simplex-method}
\end{figure}